Deciphering the genetic interactions between Pou4f3, Gfi1 and Rbm24 in maintaining cochlear hair cell survival

Version 1

Abstract

Abstract

Mammals have limited sound receptor hair cells (HCs) that cannot be regenerated after damage. Thus, investigating the molecular mechanisms underlying how to maintain HC survival is crucial to prevent hearing impairment. The Pou4f3-/-or Gfi1-/- HCs initially form but rapidly degenerate, whereas Rbm24-/- HCs degenerate much later. It remains elusive about the transcriptional cascades among Pou4f3, Gfi1 and Rbm24. Here, we demonstrate that Rbm24 expression is completely repressed in Pou4f3-/- HCs, but its expression is not altered in Gfi1-/-HCs. Moreover, both Pou4f3 and Gfi1 expressions are intact in Rbm24-/-HCs. Moreover, by the in vivo mouse transgenic reporter assays, we identify three Rbm24 enhancers to which Pou4f3 binds. Finally, we test whether Rbm24 restoration can alleviate degeneration of Pou4f3-/- HCs. Our in vivo genetic assay shows that ectopic Rbm24 alone is unable to stop Pou4f3-/- HCs from undergoing degeneration. Collectively, our study provides new molecular and genetic insights into how HC survival is regulated.

Introduction

Housed in the mammalian cochlea, the auditory epithelium, also referred to as the Organ of Corti (OC), contains the mechanosensory receptors hair cells (HCs) that detect sound information 1, 2. Two types of HCs exist: inner HCs (IHCs) and outer HCs (OHCs), with one row of IHCs and three rows of OHCs 3. OHCs and IHCs derive from the cochlear progenitors experiencing high level of Atoh1, a master transcription factor (TF) in HC development 4–6. No HCs are formed in Atoh1 -/- cochleae, highlighting the essential roles of Atoh1 in specifying the general HC fates in the undifferentiated progenitors 7, 8. OHCs uniquely express motor protein Prestin (encoded by Slc26a5) and serve as sound amplifiers 9, 10. In contrast, IHCs specifically express Fgf8, vGlut3 (encoded by Slc17a8) and Otoferlin 11–15, acting as the primary sensory cells that form synapses with different subtypes of type I spiral (auditory) neurons 16–19. Insm1 is necessary in stabilizing OHC fate, and ∼50% of Insm1-/- OHCs tend to transdifferentiate into IHC-like cells 20, 21. Ikzf2 is not needed in early OHC development but is required in consolidating the OHC fate, and Ikzf2 cello/cello deficient OHCs are dysfunctional and misexpress IHC genes 22. Insm1 is an epistatic but indirect positive regulator of Ikzf2, and restoration of Ikzf2 can partially mitigate the phenotypes of Insm1-/- OHCs 21. In contrast to Insm1 and Ikzf2, Tbx2 is required in IHC fate specification, differentiation, and maintenance, and IHC to OHC conversion occurs in the absence of Tbx2 23–25.

It is necessary to maintain the survival of cochlear HCs after their production. Pou4f3, a POU-domain family TF and known hearing loss gene (DFNA15), is essential for HCs to survive 26–30. Different from Atoh1, Pou4f3 is not involved in fate determination of HCs 31. As one target gene regulated by Atoh1 27, 32, Pou4f3 is turned on in HCs between E14.5 and E16 in a basal to apical gradient, and subsequently Pou4f3 activates Gfi1, another zinc finger TF 33, 34. Gfi1 becomes undetectable in Pou4f3-deficient HCs 34. HCs, especially the OHCs, degenerate in Pou4f3 and Gfi1-mutants by birth 34. Besides Pou4f3 and Gfi1, RNA binding protein Rbm24 is also specifically expressed in cochlear HCs 35. Our recent study shows that Rbm24 is indispensable in maintaining the survival of OHCs, but the OHC death happens much later than the case in Pou4f3 and Gfi1-mutants, with OHCs develop normally by birth but the majority of them undergo cell death by postnatal day 19 (P19) in Rbm24-/- mice 36. It remains elusive about how Rbm24 is regulated during cochlear HC development.

The similar but delayed phenotype of OHC death in Rbm24 mutants relative to Pou4f3 and Gfi1-deficient mice prompted us to dissect the potential genetic interactions among them by utilizing in vivo genetic approach. Our data clearly showed that onset of Rbm24 expression was completely repressed in Pou4f3-/- HCs. Surprisingly, Rbm24 expression was normal in Gfi1-/- HCs. Moreover, neither Pou4f3 nor Gfi1 expression was altered in the Rbm24-/- HCs. Thus, our data showed that Pou4f3, but not Gfi1, is required in Rbm24 expression. Furthermore, we identified three Rbm24 enhancers that were sufficient to drive specific EGFP reporter expression in HCs, which are likely bound by Pou4f3. Finally, restoration of Rbm24 alone cannot alleviate the degeneration of Pou4f3-/- HCs, highlighting that additional targeted genes of Pou4f3 are needed to be restored before keeping Pou4f4-/-HCs able to survive. In sum, our study provides new insights into the genetic interactions among Pou4f3, Gfi1 and Rbm24, with potential applications into HC protection.

Results

Rbm24 expression is completely repressed in Pou4f3 -/- cochlear HCs

HC degeneration happens in both Pou4f3-/- and Rbm24-/- mice, with the phenotypes occur earlier and are more severe in Pou4f3-/- mice 34, 36. It prompted us to speculate that genetic interaction between Pou4f3 and Rbm24 exists. Given Pou4f3 is the upstream positive regulator of Rbm24, Rbm24 expression should be blocked in the absence of Pou4f3. To rapidly determine whether it is the case, we took advantage of our previously established CRISPR-stop approach 37. As illustrated in Supplemental Figure 1A, co-injecting one sgRNA-1 against Pou4f3 and base editor components in one-cell stage mouse zygotes yielded founder 0 (F0) mice whose tail DNA was subjected to sanger sequencing. Relative to wild type (WT) mice (Supplemental Figure 1B), the F0 mice carrying the homozygous premature emergence of stop codon (TAG) were defined as Pou4f3-/-mice that were immediately ready for phenotypic analysis (Supplemental Figure 1C).

Triple staining of Pou4f3, Rbm24 and Insm1 demonstrated that OHCs were Pou4f3+/Rbm24+/Insm1+, and IHCs expressed Pou4f3 and Rbm24, but not Insm1 in basal turn of WT mice at E16.5 (n=3, Supplemental Figure 1D-D’’’). Pou4f3 expression was completely absent in the Pou4f3 -/- mice (n=9, Supplemental Figure 1E-E’’’), confirming that Pou4f3 translation was blocked. Different from WT mice, Rbm24 expression completely disappeared in the Pou4f3 -/- mice at E16.5 (Supplemental Figure 1E-E’’’). Notably, Insm1 expression seemed normal in Pou4f3 -/- mice (arrows in Supplemental Figure 1E-E’’’), although we noticed that the alignment of Insm1+ OHCs was not as regular as the WT OHCs (Supplemental Figure 1D-D’’’). Moreover, the presence of Insm1+ OHCs in the Pou4f3 -/- mice ruled out the possibility that the absence of Rbm24 was due to a secondary effect of OHC death or delayed differentiation, and also agreed with previous report that initial HC differentiation can occur without Pou4f3 31, 34. Thus, the rapid Pou4f3 loss-of-function analysis by CRISPR-stop supports our hypothesis that Pou4f3 is required in turning on Rbm24 expression.

Rbm24 expression is repressed in cochlear HCs in the absence of Pou4f3.

(A) A simple illustration of how Pou4f3 -/- strain was generated. (B) One exampled tail PCR gel image that helped us to distinguish WT (Pou4f3+/+), heterozygous (Pou4f3+/-) and homozygous (Pou4f3-/-) mice. (C-F’’’) Triple straining of Rbm24, Pou4f3 and Bcl11b in WT (C and E-E’’’) and Pou4f3-/- (D and F-F’’’) mice (n=3 for each) at E16.5, with only Rbm24 (green) channel was visualized in (C and D) at low magnification. (E-E’’’) and (F-F’’’) were the high magnification images of middle turn WT and Pou4f3-/- mice, respectively. In the absence of Pou4f3, Rbm24 expression completely disappeared, despite nascent Bcl11b+ OHCs were present. OHC: outer hair cell; IHC: inner hair cell. Scale bars: 100 μm (D), 20 μm (F’’’).

To further validate the observation above, we also constructed a germ line stable Pou4f3 mutants in which the entire Pou4f3 genome between sgRNA-2 and sgRNA-3 was deleted (Figure 1A). The three genotypes of Pou4f3+/+, Pou4f3+/- and Pou4f3-/- were readily distinguished by tail DNA PCR (Figure 1B). Relative to WT mice (n=3, Figure 1C), Rbm24 again was completely absent in Pou4f3-/- mice at E16.5 (n=3, Figure 1D). Like Insm1, Bcl11b is another OHC marker 20. Triple staining of Rbm24, Pou4f3 and Bcl11b also demonstrated that, relative to WT HCs (Figure 1E-E’’’), Rbm24 was completely absent in Pou4f3-/- HCs (Figure 1F-F’’’). Presence of Bcl11b+ OHCs also confirmed that production of nascent OHCs were normal in the absence of Pou4f3. Moreover, in contrast to WT mice at P1 (n=3, Supplemental Figure 2A-A’’), HC degeneration was manifest in the germ line Pou4f3-/- mutants at P0 (n=4, Supplemental Figure 2B-B’’) and P1 (n=3, Supplemental Figure 2C-C’’). By normalizing numbers of the remaining HCs in Pou4f3-/-mice at P0 or P1 to those in WT mice at P1, we found that in P0 Pou4f3-/- mice, 35.94% ± 4.52%, 38.16% ± 2.79% and 63.8% ± 5.28% HCs survived in basal, middle and apical turns, respectively. However, in P1 Pou4f3-/-mice, 5.54% ± 3.11%, 15.79% ± 3.65% and 65.64% ± 7.95% of the HCs respectively survived in basal, middle and apical turns. Thus, HC degeneration at middle and basal turns was more severe (** p<0.01) at P1 than that at P0, but there was no significant difference in apical turns (Supplemental Figure 2D).

Gfi1 is dispensable for Rbm24 expression.

(A) A simple cartoon representing how the Gfi1 was inactivated in the one-cell stage mouse zygotes derived from male Gfi1HACre/+ by the CRISPR-stop approach. (B-C) With sgRNA-6 as an example, the Sanger sequencing chromatograms of control Gfi1HACre/+ (B) and F0 Gfi1-/- (C) were presented. The base ‘C’ (black arrow in B) was converted in ‘T’ (red arrow in C), resulting in pre-emergence of protein translation stop codon TAG. The red ‘T’ was a single peak, meaning that the pre-emergence of stop codon occurred in both alleles. (D-E’’) Dual staining of HA (Gfi1) and Rbm24 in cochleae from control Gfi1HACre/+(D-D’’, n=3) and F0 Gfi1-/- (E-E’’) mice (n=4) at E16.5. Rbm24 expression (E’) was not altered in the absence of the HA (Gfi1) expression (E). OHC: outer hair cell; IHC: inner hair cell. Scale bar: 20 μm.

Different from WT cochleae in which all Myo7a+ HCs expressed Rbm24 (Supplemental Figure 2E-E’’), in Pou4f3-/- cochleae the remaining HCs lost Rbm24 expression (arrows in Supplemental Figure 2F-F’’). Collectively, our data from two different Pou4f3-deficient models support that Pou4f3 is indispensable for turning on Rbm24. Nonetheless, whether Gfi1 is also essential for Rbm24 expression remains to be determined.

Construction of a Gfi1-3× HA-P2A-Cre/+ knockin mouse strain

We determined whether the regulation of Rbm24 by Pou4f3 through Gfi1 or independently of Gfi1. Due to lack of a good commercial Gfi1 antibody suitable for immunostaining, we decided to construct a Gfi1-3× HA-P2A-Cre/+ (Gfi1HA-Cre/+ in brief) knockin mouse strain via our routine CRISPR/Cas9 approach (Supplemental Figure 3A-C). In principle, the C-terminus of Gfi1 was tagged with three HA fragments, and the Cre is under the endogenous cis-regulatory elements of Gfi1. The WT (Gfi1+/+), heterozygous (Gfi1HA-Cre/+) and homozygous (Gfi1HA-Cre/HA-Cre) mice were readily distinguished by tail PCR (Supplemental Figure 3D). In addition to the Gfi1 locus, Southern blot assay showed that random insertion of the targeting vector (Supplemental Figure 3B) happened in the unknown genomic region. Nonetheless, it was likely that the random insertion happened in a silent genomic region, which was evidenced by the analysis below.

Pou4f3 and Gfi1 expressions are normal in the absence of Rbm24.

(A) A simple cartoon to elaborate how we used CRISPR-stop approach to induce mosaic inactivation of Rbm24 in the one-cell stage mouse zygote harboring Gfi1HACre/+. Notably, the injection was in the late one-cell stage of the zygotes, resulting in higher rates of final mosaic inactivation. (B-C) The Sanger sequencing chromatograms of control Gfi1HACre/+; Rbm24+/+ (B) and Gfi1HACre/+; Rbm24-/- (mosaic) (C). The base ‘C’ (black arrow in B) was converted into ‘T’ (red arrow in C) in a fraction of cochlear cells. Notably, the mosaic inactivation of Rbm24 was evidenced by the double peaks of ‘T’ and ‘C’ (red arrow in C). (D-E’’’) Triple staining of Rbm24, HA and Pou4f3 in cochlear samples (basal turns) of control Gfi1HACre/+; Rbm24+/+(D-D’’’, n=3) and Gfi1HACre/+; Rbm24-/- (mosaic) (E-E’’’, n=3) at E17. Consistent with the Sanger sequencing results (C), Rbm24 was inactivated in cochlear HCs in a mosaic pattern (E). The orange arrows (E-E’’’) pointed to one OHC that lost Rbm24, whereas the blue arrows (E-E’’’) marked one OHC in which the Rbm24 expression was maintained. Notably, regardless of whether Rbm24 was inactivated or not, HA (Gfi1) and Pou4f3 expression were not altered. OHC: outer hair cell; IHC: inner hair cell. Scale bar: 20 μm (E’’’).

Dual staining of HA (Gfi1) and pan-HC marker Myo7a demonstrated that, similar to Gfi1+/+ mice (n=3, Supplemental Figure 3E-E’’), HC development in Gfi1HA-Cre/HA-Cre was normal at P1 (n=3, Supplemental Figure 3F-F’’). Moreover, HA (Gfi1) was highly expressed in all Myo7a+ IHCs and OHCs in Gfi1HA-Cre/HA-Cre mice (arrows in Supplemental Figure 3F-F’’). It confirmed that Gfi1 endogenous expression is not affected in the Gfi1HA-Cre/HA-Cre mice, representing an advantage over the previous Gfi1Cre/+ strain where one copy of Gfi1 is lost and early onset of hearing loss happens in Gfi1Cre/+ 38, 39.

We additionally performed the fate mapping analysis of Gfi1HA-Cre/+; Rosa26-loxp-stop-loxp-tdTomato (Ai9)/+ (Gfi1HA-Cre/+; Ai9/+) at P2. The Gfi1HA-Cre/+; Ai9/+ model allowed us to both visualize temporal Gfi1 protein expression pattern and permanently mark cells experiencing Gfi1 expression with tdTomato. Neither tdTomato nor HA was detected in the Myo7a+ HCs of the control Ai9/+ mice (n=5, Supplemental Figure 3G-G’’’ and I-I’’). In contrast, majority of the Myo7a+ HCs expressed tdTomato and HA in the Gfi1HA-Cre/+; Ai9/+ mice (n=5, Supplemental Figure 3H-H’’’ and J-J’’). We noticed that the general HA (Gfi1) expression level in IHCs seemed higher than that in OHCs (Supplemental Figure 3J-J’’). Moreover, HA (Gfi1) expression levels exhibited manifest heterogeneities among OHCs. The OHCs expressing the highest (#1), intermediate (#2) and lowest (#3) levels of HA (Gfi1) were respectively marked (arrows in Supplemental Figure 3J-J’’). Notably, such a heterogenous Gfi1 expression in neonatal HCs was not observed in Gfi1HA-Cre/HA-Cre mice (Supplemental Figure 3F-F’’), likely due to the higher level of HA tagged Gfi1 in Gfi1HA-Cre/HA-Cre than in Gfi1HA-Cre/+ mice. Besides HCs, tdTomato+ cells were present in the non-sensory regions (arrows in Supplemental Figure 3H), consistent with the previous report 38. Collectively, Gfi1HA-Cre/+ strain was suitable to visualize Gfi1 protein by HA antibody, albeit random insertion of the targeting vector existed. Alternatively, Gfi1HA-Cre/+ at least can be treated as a pseudo transgenic mouse strain, by which we can reliably visualize Gfi1 and trace cells experiencing Gfi1 expression.

Gfi1 expression is prohibited in the Pou4f3-/- cochlear HCs

Given HA can faithfully represent the Gfi1 expression in the Gfi1HA-Cre/+, HA expression was expected to be repressed in the Pou4f3-/- HCs, as reported by previous studies 33, 34. We confirmed this predication by our CRISPR-stop approach 37. Basically, the pipeline was identical to the production of Pou4f3 mutants described above (Supplemental Figure 1), except that here the zygotes were derived from male Gfi1HA-Cre/+ mice (Supplemental Figure 4A). We obtained the mosaic (or chimeric) Pou4f3-/- mice, which was confirmed by Sanger sequencing of tail PCR (Supplemental Figure 4B and C), partly due to the injection time was the late stage of one-cell stage zygotes. In control Gfi1HA-Cre/+ mice, there was a pure ‘C’ base (blue arrow in Supplemental Figure 4B), however, a mixture of ‘C’ and ‘T’ double peaks existed in Gfi1HA-Cre/+; Pou4f3-/- (mosaic) mice (red arrow in Supplemental Figure 4C). Nonetheless, the advantage of the mosaic Pou4f3-/- mice was that it allowed us to have internal control Pou4f3+/+ and Pou4f3-/- HCs in the same cochlea, and to determine the phenotype occurs in a cell autonomous or non-cell autonomous manner.

Three Rbm24 enhancers are sufficient to drive specific EGFP expression in cochlear HCs.

(A) Visualization of ATAC-seq (top row, orange color) of P1 cochlear HCs (from our previous study, GSE181311) and Pou4f3 Cut&Run assay (bottom row, blue color) of E17.5 cochlear HCs (from another study, GSE150391) by Integrative Genomics Viewer. The black arrow marked the Rbm24 promoter, and the three Rbm24 enhancers (Eh1, Eh2 and Eh3) were marked by the dotted square. (B-G’’) Dual staining of EGFP and Myo7a in Eh1-EGFP+ (B-C’’, n=7), Eh2-EGFP+ (D-E’’, n=6) and Eh3-EGFP+ (F-G’’, n=4) at P1. Only the EGFP channel was visualized in whole mount staining (B, D, F). In the cryosection cochlear samples, EGFP was overlapped with HC marker Myo7a. OHCs: outer hair cells; IHC: inner hair cell. Scale bars: 100 μm (F), 20 μm (G’’).

In control Gfi1HA-Cre/+ mice (n=3) at E16.5, all HCs expressed Pou4f3, Rbm24 and HA(Gfi1), albeit HA (Gfi1) levels again seemed heterogenous among the OHCs (Supplemental Figure 4D-D’’’). In contrast, in the Gfi1HA-Cre/+; Pou4f3-/- (mosaic) mice (n=3), we captured HCs that lost or maintained Pou4f3 expression (Supplemental Figure 4E-E’’’). Notably, Pou4f3+ HCs expressed HA(Gfi1) and Rbm24 (blue arrows in Supplemental Figure 4E-E’’’), in contrast, both HA(Gfi1) and Rbm24 disappeared in HCs that lost Pou4f3 expression (orange arrows in Supplemental Figure 4E-E’’’). Thus, our data clearly confirmed that HA indeed was a reliable readout for Gfi1 expression and was sensitive to loss of Pou4f3. Moreover, it supported that Pou4f3 regulates Rbm24 in a cell autonomous manner.

Gfi1 is dispensable for Rbm24 expression

Next, we produced Gfi1-/- mutants by the same CRISPR-stop approach 37. One-cell stage zygotes derived from male Gfi1HA-Cre/+ mice were injected with base editor components and 4 different sgRNAs located in different exons of Gfi1 (Figure 2A). The reason why 4 sgRNAs were combined was elaborated in the discussion part. With sgRNA-6 as an example, Sanger sequencing of tail DNA demonstrated that, relative to control Gfi1HA-Cre/+ mice (black arrow in Figure 2B), premature emergence of TAG stop codon happened in F0 mice, resulting in homozygous Gfi1 inactivation (red arrow in Figure 2C). All HCs expressed HA (Gfi1) and Rbm24 in control Gfi1HA-Cre/+ mice (n=3, Figure 2D-D’’). Notably, Rbm24 expression was maintained in the Gfi1-/- HCs that lost HA (Gfi1) at E16.5 (n=4, Figure 2E-E’’). It suggested that Rbm24 expression is not dependent on Gfi1.

The advantage of the above Gfi1-/- model was rapid and direct confirming the absence of Gfi1 expression in the F0 mice. However, we cannot guarantee that all HCs completely lost Gfi1 expression at the single cell resolution via HA staining, because only one allele of Gfi1 was Gfi1HA-Cre. Thus, to rule out the possibility that only the HA tagged Gfi1 allele was mutated, we further generated the germ line stable Gfi1 mutants in which its majority DNA fragments between sgRNA-4 and sgRNA-9 were deleted (Supplemental Figure 5A). The WT (Gfi1+/+), Gfi1+/- and Gfi1-/- mice were readily to be identified by tail PCR (Supplemental Figure 5B). Consistent with previous reports 40, dual staining of Rbm24 and Pou4f3 showed that, relative to WT mice (n=3, Supplemental Figure 5C-C’’), severe degeneration of HCs, especially of the OHCs, was present in the Gfi1-/- mice (n=3, Supplemental Figure 5D-D’’). It validated the success of generating the Gfi1-/- mice. Notably, the surviving Pou4f3+ HCs kept the expression of Rbm24 (orange arrows in Supplemental Figure 5D-D’’). In contrast, no significant difference was observed between WT and Gfi1-/- mice at E16.5, as both WT and Gfi1-/-HCs expressed Pou4f3 and Rbm24, and both WT and Gfi1-/- OHCs expressed Bcl11b (Supplemental Figure 5E-F’’’). It suggests that degeneration of Gfi1-/- HCs does not begin by E16.5. Presence of Pou4f3 in Gfi1-/-HCs agreed with previous notion that Pou4f3 is epistatic to Gfi1. Collectively, analysis of both Gfi1 mutant models supports that Gfi1 is dispensable for Rbm24 expression.

Forced expression of Rbm24 fails to rescue the OHC degeneration in Pou4f3-/- mutants.

(A) Generation of Rosa26-Loxp-stop-Loxp-Rbm24*3ξHA/+ (Rosa26Rbm24/+) mouse stain. The C-terminus of the ectopic Rbm24 was tagged with three HA tags. (B) One exampled tail PCR gel image that helped us to distinguish WT (+/+) and KI (Rosa26Rbm24/+) mice. (C-F’’) Dual staining of HA (Rbm24) and hair cell marker Myo7a in mice with four different genotypes at P1: Pou4f3+/+ (C-C’’, n=3), Pou4f3-/- (D-D’’, n=3) and Pou4f3+/+; Atoh1Cre/+; Rosa26Rbm24/+(E-E’’, n=3) and Pou4f3-/-; Atoh1Cre/+; Rosa26Rbm24/+ (F-F’’, n=3). The ectopic HA (Rbm24) was not detected in Pou4f3+/+ (C) and Pou4f3-/- (D), but was detected in both Pou4f3+/+; Atoh1Cre/+; Rosa26Rbm24/+(E) and Pou4f3-/-; Atoh1Cre/+; Rosa26Rbm24/+(F). The white arrows in (E-E’’) pointed to one Myo7a+ IHC that expressed the ectopic HA (Rbm24). The HCs seemed normal by P1, despite the ectopic Rbm24 expression was induced. The orange arrows in (E-E’’) labelled one SC that expressed HA (Rbm24) but not Myo7a. The white arrows in (F-F’’) should be one remaining Myo7a+ HC that expressed ectopic Rbm24. Overall, many of the Pou4f3-/- HCs degenerated, albeit ectopic Rbm24 was induced. OHC: outer hair cell; IHC: inner hair cell; HC: hair cell. Scale bar: 20 μm (F’’).

Pou4f3 and Gfi1 expressions are normal in Rbm24-/- cochlear HCs

Given that Pou4f3 is upstream and positive regulator of Rbm24, we predicted that Pou4f3 expression should be unaffected in the Rbm24-/- HCs. To determine whether the predication was correct or not, we established the Rbm24-/- mouse strain by injecting one Rbm24 sgRNA (sgRNA-10) into one-cell stage zygotes derived from male Gfi1HA-Cre/+ mice (Figure 3A). We chose Gfi1HA-Cre/+ zygotes in order to simultaneously assess Gfi1 and Pou4f3 expression patterns in Rbm24-/- HCs. Relative to the control Gfi1HA-Cre/+; Rbm24+/+ (Figure 3B), premature emerge of the TAG stop codon appeared in the Gfi1HA-Cre/+; Rbm24-/- (mosaic) mice (Figure 3C). Notably, Sanger sequencing of tail DNA showed that the Rbm24 mutation was mosaic, as mixed ‘T’ and ‘C’ peak existed (red arrow in Figure 3C).

The mosaic inactivation of Rbm24 was further confirmed by triple staining of Rbm24, HA and Pou4f3 (Figure 3D-E’’’). Relative to control Gfi1HA-Cre/+; Rbm24+/+ (n=3, Figure 3D-D’’’), Rbm24 expression disappeared in a fraction of cochlear HCs (orange arrows in Figure 3E-E’’’) but remained normal in other HCs (blue arrows in Figure 3E-E’’’) of the Gfi1HA-Cre/+; Rbm24-/- (mosaic) mice (n=3) at E17. Notably, regardless of whether Rbm24 was inactivated or not in the cochlear HCs, both HA (Gfi1) and Pou4f3 expression patterns were intact. It supports that Pou4f3 is epistatic to Rbm24 and deletion of Rbm24 does not affect Pou4f3 expression. Moreover, our data suggests that Gfi1 and Rbm24 do not have genetic interactions. Gfi1 inactivation did not affect Rbm24 (Figure 2 and Supplemental Figure 5), and vice versa (Figure 3E-E’’’).

Three Rbm24 enhancers can drive specific EGFP expression in cochlear HCs

After showing that Pou4f3, but not Gfi1, is indispensable in mediating Rbm24 expression, we next determined the mechanism underlying how Pou4f3 controls Rbm24 expression, in particular, the cis-regulation elements (CREs) of Rbm24. According to our previous Transposase-Accessible Chromatin with high-throughput sequencing (ATAC-seq) of neonatal cochlear HCs 8, four CREs of Rbm24 were identified: one proximal promoter (arrow in Figure 4A) and three distal ones that were potential enhancers and defined as Eh1, Eh2 and Eh3, respectively (dotted square in Figure 4A). Eh1 and Eh2 were distributed upstream, whereas Eh3 was downstream of Rbm24 coding region. Moreover, we reanalyzed the Pou4f3 Cut&Run assay from one previous study 32, and found that Pou4f3 binds to Eh1, Eh2 and Eh3, but not to the Rbm24 promoter (Figure 4A).

Whether Eh1, Eh2 and Eh3 are bona-fide Rbm24 enhancers remain to be determined. We reasoned that, if Eh1, Eh2 and Eh3 were Rbm24 enhancers, either of them, together with the mini promoter of mouse heat shock protein 68 (Hsp68) 8, 41–43, would be sufficient to drive specific reporter expression in cochlear HCs. To address this question, we established three transgenic mouse strains: Eh1-EGFP+ (n=7, Figure 4B-C’’), Eh2-EGFP+ (n=6, Figure 4D-E’’) and Eh3-EGFP+ (n=4, Figure 4F-G’’). Briefly, in each strain the EGFP expression was driven by the mini promoter of Hsp68 and Eh1 (or Eh2 or Eh3). It is known that the mini promoter of Hsp68 alone is not able to drive EGFP expression 44. In contrast, strong EGFP expression was observed by whole mount analysis in all three transgenic lines (Figure 4B, D and F). Moreover, dual staining of EGFP and Myo7a in cryosectioned cochleae showed that EGFP was specifically expressed in IHCs and OHCs in all three strains at P1 (Figure 4C-C’’, E-E’’ and G-G’’). Collectively, our transgenic assay supports that Eh1, Eh2 and Eh3 are Rbm24 enhancers. Moreover, Pou4f3 mediates the Rbm24 expression primarily by binding to Rbm24 enhancers.

Forced Rbm24 expression fails to alleviate the degeneration of Pou4f3-/-HCs

Whether ectopic Rbm24 expression can alleviate the degeneration of Pou4f3-/- HCs remains unknown, albeit we showed that Rbm24 is certainly regulated by Pou4f3. Thus, we established a new conditional Rosa26-Loxp-stop-Loxp-Rbm24*3xHA/+ (Rosa26Rbm24/+ in short) mouse model (Figure 5A and B). To turn on ectopic Rbm24 in cochlear HCs, Rosa26Rbm24/+ was further crossed with the Atoh1Cre/+ that targets majority of cochlear HCs and a fraction of SCs 39. Notably, in the Rosa26Rbm24/+strain, Rbm24 was tagged with three HA fragments, which facilitated us to distinguish the endogenous and the ectopic Rbm24. In the control Pou4f3+/+ (Figure 5C-C’’) and the germ line stable Pou4f3-/- (Figure 5D-D’’) mice, the Myo7a+ HCs did not express HA (Rbm24), however, almost of all Myo7a+ HCs expressed HA (Rbm24) in the Pou4f3+/+; Atoh1Cre/+; Rosa26Rbm24/+mice at P1 (white arrows in Figure 5E-E’’). As expected, besides HCs, we captured a few SCs expressing HA (Rbm24) but not Myo7a (orange arrows in Figure 5E-E’’). Those cochlear HCs expressing HA (Rbm24) seemed normal, suggesting that they can tolerate extra Rbm24 expression by P1. Collectively, it supports that the Rosa26Rbm24/+model was successfully generated and ectopic Rbm24 was induced in cochlear HCs in Pou4f3+/+; Atoh1Cre/+; Rosa26Rbm24/+.

In contrast to our expectation, ectopic Rbm24 expression failed to mitigate the degeneration of Pou4f3-/- HCs. Severe degeneration of HCs (both IHCs and OHCs) occurred in Pou4f3-/-; Atoh1Cre/+; Rosa26Rbm24/+(Figure 5F-F’’), indistinguishable from the Pou4f3-/-mice (Figure 5D-D’’), except that the remaining HCs expressed Rbm24 in the Pou4f3-/-; Atoh1Cre/+; Rosa26Rbm24/+ (arrows in Figure 5F-F’’). It suggests that restoration of Rbm24 alone is not sufficient to prevent Pou4f3-/- cochlear HCs from undergoing degeneration.

Discussion

Molecular mechanisms underlying cochlear HC survival

Our sound receptor HCs are vulnerable to various genetic mutations, environmental ototoxic factors and ageing. The degeneration of HCs is one of the primary reasons accounting for human sensorineural hearing impairment 45. Previous studies have revealed many genes whose mutations lead to HC degeneration starting at different ages. Severe HC developmental defect happens in Atoh1 -/- mutants 7, 46. It is known that Atoh1-/- cochlear sensory cells undergo apoptosis. Whether the absence of HCs in Atoh1-/- mice is due to that HCs are never produced, or immediately die after initial emergence remains unclear, partly due to the difficulty of unambiguously defining the nascent HCs by molecular markers.

Differently from Atoh1-/- mutants, in both Pou4f3-/-and Gfi1-/- mice 31, 33, 34, the initial cochlear HC development is normal but become defective at perinatal ages, consistent with the notion that Pou4f3 and Gfi1 are not required in HC fate specification but needed in subsequent differentiation and survival. It is known that caspase 3 is active during the hair cell death in the Pou4f3-/- mutants, and the anti-apoptotic factor z-VAD-fmk has a protective effect on the Pou4f3-/-HCs between 14.5 and E16.5 47. Moreover, we noticed that the overall HC degeneration in Gfi1-/- was milder than in Pou4f3-/- mice at P1, because only OHC degeneration happened in the Gfi1-/-, but both IHC and OHC were degenerated in Pou4f3-/- mice (Supplemental Figures 2 and 5).

It is known that Gfi1 is the target of Pou4f3 34. Whether forced Gfi1 expression can alleviate the degeneration of Pou4f3-/- HCs remains unknown, too. Likewise, Pou4f3 is one of the target genes regulated by Atoh1 32, however, whether forced expression of either Pou4f3 or Gfi1, or both Pou4f3 and Gfi1, is able to mitigate the developmental defects of Atoh1-/- HCs remains to be determined. Future studies are warranted to resolve those remaining questions before further deeply understanding the mechanisms underlying how to keep cochlear HCs to survive.

Roles of Rbm24 and how Rbm24 is regulated during cochlear HC development

Shortly after cochlear HCs emerge, Rbm24 is expressed and permanently maintained, evidenced by transcriptomic analyses and antibody staining 23, 35, 48–50. Rbm24 is not necessary in early phase of cochlear HC development, because Rbm24-/-HC development is normal by P1, however, Rbm24 is required for OHC to survive after birth 36. Rbm24-/- OHCs, but not IHCs, are degenerated by P19 36. Rbm24 is also involved in mRNA stability and pre-mRNA alternative splicing of genes including Cdh23 and Pcdh15 that are crucial for HC stereocilia development 51–53. Nonetheless, the single-cell transcriptomic analysis of Rbm24-/- IHCs or OHCs is not yet available and the detailed molecular mechanism underlying Rbm24-/-HC degeneration remains to be clarified in future studies.

What are the trans-acting factors that are involved in regulating Rbm24 expression? First, our current study provided strong genetic evidence to support that Pou4f3 is needed in turning on Rbm24. In the absence of Pou4f3, Rbm24 expression cannot be triggered. The normal expression of Pou4f3 in Rbm24-/- HCs further confirmed that Pou4f3 is epistatic to Rbm24 and that Rbm24 is dispensable for Pou4f3 expression. Besides Pou4f3, the engagement of Atoh1 in Rbm24 regulation is supported by two lines of evidence: one is that Rbm24 expression disappears in the Atoh1-/- cochlear HCs 54; the second is that Rbm24 belongs to the Atoh1 binding targets revealed by Atoh1 Cut&Run assay 8, 32. Notably, Atoh1 binds both Rbm24 promoter and its three enhancers Eh1, Eh2 and Eh3 8, 32, which differs with Pou4f3 which only binds Rbm24 enhancers (Figure 4). Thus, it is likely that Pou4f3 and Atoh1 cooperate to regulate Rbm24, and either Pou4f3 or Atoh1 mutation leads to repression of Rbm24 expression. Whether Rbm24 expression in adult HCs needs Pou4f3 remains to be determined by future conditional Pou4f3 loss-of-function studies.

Gfi1 and Rbm24 expression are independent to each other

We initially hypothesized that Pou4f3 mediated Rbm24 expression through Gfi1. However, this hypothesis is not supported by the observation that Rbm24 expression is normal in the Gfi1-/- HCs (Figure 2 and Supplemental Figure 5). Moreover, in the absence of Rbm24, Gfi1 expression is not altered in cochlear HCs, either. Thus, Rbm24 and Gfi1 expressions seem independent to each other. It might be due to the functional difference between Pou4f3 and Gfi1 during cochlear HC development. Both Pou4f3 and Gfi1 are needed in promoting expression of genes involved in HC differentiation 28, 30, 34, 40, however, Gfi1, but not Pou4f3, also represses the preceding neural genes expressed in nascent HCs 40.

Furthermore, we have another observation relevant to Gfi1 isoforms that is worthy of discussion. Our previous report shows that one efficient sgRNA is enough to induce homozygous gene inactivation by CRISPR-stop 36. Notably, we used 4 different Gfi1 sgRNAs that are distributed in different exons (Figure 2A). We indeed successfully established one Gfi1 mutant by using the sgRNA-5 alone which in principle would effectively pre-stop the Gfi1 translation in exon 1 coding SNAG repressor domain. This Gfi1 mutant (sgRNA-5 alone) was able to yield the HC degeneration phenotype, but the HA (Gfi1) was still detectable in HCs. It is consistent with the notion that Gfi1 mutant lacing the SNAG domain is equivalent to Gfi1-null model 55. Thus, it is likely that Gfi1 has multiple unknown isoforms, many of which might be recognized by the HA tag antibody because HA is tagged in the last exon 6. When 4 Gfi1 sgRNAs were combined, we were able to both reproduce the HC degeneration phenotype and completely block the HA (Gfi1) expression.

Why does ectopic Rbm24 fail to alleviate the degeneration of Pou4f3-/- HCs?

After confirming the epistatic genetic interaction between Pou4f3 and Rbm24, we predicted that ectopic Rbm24 expression should be able to, at least partly, alleviate the degeneration of Pou4f3-/- HCs, similar to the case between Insm1 and Ikzf2 in cochlear OHCs in our recent study 21. However, the actual observation is that Rbm24 failed to rescue the HC degeneration in the Pou4f3-/-mice. There are two possible interpretations: 1) Despite it is regulated by Pou4f3, Rbm24 is not directly involved in the pathway regulating HC survival. Indeed, the cell death in Rbm24-/- HCs happens later than in Pou4f3-/- HCs; 2) Although Rbm24 is a key Pou4f3 downstream target, its forced expression alone cannot compensate loss of Pou4f3 or other known Pou4f3 targets such as orphan thyroid nuclear receptor Nr2f2 and Caprin-1 56, 57. Caprin-1 is recruited to stress granules in cochlear HCs exposed to ototoxic trauma 57.

The potential application of the three Rbm24 enhancers in cochlear HC gene therapy

Gene therapy is a promising strategy to restore the hearing capacity in human inheriting gene mutations 45. A few examples have been reported, including Otoferlin and vGlut3 gene replacement 58–61. Currently, the therapeutic cDNAs were primarily delivered into HCs with an adeno-associated virus (AAV) vector. Despite many AAVs are reported 62, 63, their transfecting cochlear cells is non-selective and HC specific AAV is not available yet. One solution is that, instead of the CAG/CMV ubiquitous promoter widely used in current AAVs 64, 65, either of the three Rbm24 enhancers together with Hsp68 mini promoter (in brief Rbm24-Hsp68) should be able to produce an AAV that would specifically transfect HCs. Moreover, Rbm24 is permanently expressed in cochlear HCs. Given the Rbm24-Hsp68 AAV works as expected, it would be a powerful tool for future HC specific gene therapy at all postnatal ages, with potential applications in treating clinical human deafness.

Methods and materials

Mice

The Atoh1Cre/+ model was kindly provided by Dr Lin Gan (Augusta University, USA)39. The Rosa26-loxp-stop-loxp-tdTomato (Ai9)/+ strain (Jax#: 007905) was from the Jackson Laboratory. All mice were bred and raised in a SPF-level animal room and all animal procedures were performed according to the guidelines (NA-032-2022) of the IACUC of the Institute of Neuroscience (ION), Center for Excellence in Brain Science and Intelligence Technology, Chinese Academy of Sciences.

One-step generation of homozygous Pou4f3 or Gfi1 or Rbm24 mutants by CRISPR-stop

The detailed protocol of how to use CRISPR-stop to generate homozygous gene mutants is described in our previous report 36, 37. Briefly, efficient pre-tested sgRNAs (Table S1) and hA3ABE3 were co-injected into one-cell stage mouse zygotes that were subsequently transplanted into pseudopregnant female mice giving birth to the founder 0 (F0) mice. With Sanger sequencing of tail PCR, the F0 mice with homozygous mutation (pre-emergence of protein translation stop codon) were identified and immediately ready for analysis.

Generating Pou4f3 or Gfi1-null mutants with large DNA fragment deletion by CRISPR/Cas9

To construct germ line stable null mutants of either Pou4f3 or Gfi1, Cas9 mRNA, two efficient pre-tested sgRNAs respectively located at the proximal and distal end of the targeted gene, together with a single strand DNA donor (120 bp) (Table S3), were co-injected into the one-cell stage wild type zygotes. Notably, the left half (60 bp) of the single strand DNA donor was homologous to the 5’ end, and the right half (60 bp) was to the 3’end of the targeted gene. The post-injected zygotes were transplanted into pseudopregnant females that would give birth to the F0 mice subjected to tail PCR screening (primers were listed in Table S2). The F0 mice harboring the designed large DNA deletion between the two sgRNAs were identified and further bred with wild type mice to establish the germ-line stable mutants (F1 or afterward).

Construction of the Gfi1*3×HA-P2A-Cre knockin mouse strain

The sgRNA against Gfi1 (5ʹ-ATGGACTCAAATGAGTACCC-3ʹ), Cas9 mRNA and the targeting vector (Supplemental Figure 3B) were co-injected into the one-cell stage wild type mouse zygotes. The targeting vector contained three portions, 5’ homologous arm (800 bp), 3’ homologous arm (800 bp) and the part in the middle of 5’ and 3’ arms that contained three HA fragments followed by 2A-Cre. The F0 mice with the potential gene targeting (Supplemental Figure 3C) were screened by tail PCR, followed by crossing with wild type mice to produce F1 mice. Those F1 mice were confirmed by tail PCR again, and further subjected to Southern blot. The detailed protocol of Southern blot is described in our previous report 66. Tail DNA PCR was used for routine genotyping and primers used to distinguish between KI (Gfi1HA-Cre/+) and WT alleles were F4, R5 and R6 (Table S2).

Construction of Eh1-EGFP+, Eh2-EGFP+ and Eh3-EGFP+ transgenic reporter lines

All three transgenic reporter mouse lines, Eh1-EGFP+, Eh2-EGFP+ and Eh3-EGFP+ were produced by the same experimental procedures. The core DNA sequences of each enhancer (Eh1 or Eh2 or Eh3 in Figure 4A), mRNA of PiggyBac transposase, and the PiggyBac vector (Figure 4B, D and F) were co-injected into the one-cell stage of wild type mouse zygotes. The PiggyBac vector contained Eh1/Eh2/Eh3 core DNA sequences (Table S3), mini promoter of mouse heat shock protein 68 (Hsp68) and the EGFP coding sequence. The PiggyBac vector was randomly integrated into mouse genome by the transposase. The F0 mice containing the PiggyBac vector were screened by tail PCR and further bred with wild type mice to produce germ line stable F1 transgenic reporter strains. The samples analyzed in Figure 4B-G’’ were from F1 or afterwards. Primers used for genotyping transgenic reporter strain were F8, F9 and F10 and a common primer R11 and primer sequences were listed in Table S2.

Generation of Rosa26CAG-lsl-Rbm24*3×HA/+ mouse models

The Rosa26CAG-lsl-Rbm24*3×HA/+ (Rosa26Rbm24/+) knockin mouse strain was constructed by homologous recombination mediated by CRISPR/Cas9. The pre-tested Rosa26 sgRNA (5ʹ-ACTCCAGTCTTTCTAGAAGA-3ʹ), targeting vector (Figure 5A), together with the mRNA of Cas9 were co-injected into the one-cell stage wild type mouse zygotes. Similarly, F0 mice with potentially correct gene targeting were screened by tail PCR and further bred with wild type mice to establish germ line stable F1 mice. The primers used to distinguish wild type and the KI (Rosa26Rbm24/+) alleles were F12, R13 and R14 (Table S2).

Sample processing and immunofluorescence assay

Inner ears were dissected and fixed in 4% paraformaldehyde (PFA) in PBS (E607016-0500, Sangon Biotech) at 4℃ overnight. For cochlear cryosections, inner ears were dehydrated in 30% sucrose (V900116, Sigma) at 4℃ before embedding into the optimal cutting temperature (OCT) compound (4583, SAKURA) and slices were cut with 14 μm thickness. The detailed protocol of immunofluorescent staining is described in our previous report 67. The following primary antibodies were used: anti-Rbm24 (rabbit, 1:500, 18178-1-AP, Proteintech); anti-Pou4f3 (mouse, 1:500, sc-81980, Santa Cruz); anti-Pou4f3 (rabbit, 1:500, NBP1-88349, Novus Biologicals); anti-HA (rat, 1:500, 11867423001, Roche); anti-Myo7a (rabbit, 1:500, 25-6790, Proteus Biosciences); anti-Myo7a (mouse, 1:500, MYO7A 138-1, Developmental Studies Hybridoma Bank); anti-Ctip2 (Bcl11b) (rat, 1:500, ab18465, Abcam); anti-Insm1 (guinea pig, 1:6000, a kind gift from Dr. Carmen Birchmeier from Max Delbrueck Center for Molecular Medicine, Germany); anti-GFP (chicken, 1:500, ab13970, Abcam). Different corresponding Alexa Fluor-conjugated secondary antibodies were used for detecting the primary antibodies above. Hoechst 33342 (1:1000, H3570, Thermo Fisher Scientific) was used for nuclear DNA staining.

Lastly, either whole-mount or cryosection samples were mounted with Prolong Gold antifade medium (P36930, Thermo Fisher Scientific) at room temperature for 12 h. Samples were scanned by the Nikon C2 or Nikon NiE-A1 Plus confocal microscope. ImageJ software was used to process the confocal images.

Cell quantification and statistical analysis

Before immunofluorescent staining, each cochlear sample was grossly separated into three portions but with different length. Each portion of the same cochlea was initially scanned with confocal microscope but at a low magnification (10◊lens). After calculating the total length of each cochlea, it was precisely divided into basal, middle and apical turn with equal length. Then, for cell counting in the experiments (Supplemental Figure 2D), in each turn ∼200μm length of the sensory epithelium was scanned with confocal microscope but at a high magnification (60◊lens) by which the number of HCs was counted. In the Pou4f3-/- cochleae, the percentage of the surviving HCs was calculated by normalizing the number of the remaining HCs to the counterparts in the wild type mice. All cell numbers were presented as means ± SEM. For statistical analyses, we used GraphPad Prism 6.0 software and performed Student’s t tests with Bonferroni correction.

Supporting information

eLife Assessment

In this useful study, the authors explore regulatory cascades governing mammalian cochlear hair cell development and survival. They confirm previous studies that the transcription factors Pou4f3 and Gfi1 are necessary for hair cell survival, and use compelling evidence to demonstrate that the RNA binding protein gene RBM24 is regulated by Pou4f3, but not Gfi1. These findings will be of interest to those working on hearing loss, and hold significance for viral gene delivery methods aiming to manipulate gene expression.

Reviewer #1 (Public Review):

Wang and colleagues recently demonstrated the essential role of RBM24 (RNA-binding motif protein 24a) in the development of mouse hair cells (source: https://doi.org/10.1002/jcp.31003). In this study, they further expand on their findings by revealing that Rbm24 expression is absent in Pou4f3 mutant mice but not in Gfi1 mutant mice. This observation suggests that POU4F3 acts as an upstream regulator of Rbm24. The researchers effectively demonstrate that POU4F3 can bind to and regulate Rbm24 through three distant enhancers, which are located in open chromatin regions and are bound by POU4F3. Lastly, Wang and colleagues discovered that ectopic expression of Rbm24 was unable to prevent the degeneration of POU4F3 null hair cells.

The findings in this manuscript hold great significance as they provide additional insights into the transcriptional cascades crucial for hair cell development. The discovery of enhancers capable of driving transgene expression specifically in hair cells holds promising therapeutic implications. The figures presented in the study are of excellent quality, the employed techniques are state-of-the-art, the data are accurately represented without exaggeration, and the study demonstrates a high level of rigor.

Reviewer #2 (Public Review):

Previous studies have shown that two hair cell transcription factors, Pou4f3 and Gfi1, are both necessary for the survival of cochlear hair cells, and that Gfi1 is regulated by Pou4f3. The authors have previously also shown that mosaic inactivation of the RNA-binding protein RBM24 leads to outer hair cell death.

In the present study, the authors show that hair cells die in Pou4f3 and Gfi1 mutant mice. They show that Gfi1 is regulated by Pou4f3. Both these observations have been published before. They then show that RBM24 is absent in Pou4f3 knockouts, but not Gfi1 knockouts. They ectopically activate RMB24 in the hair cells of Pou4f3 knockouts, but this does not rescue the hair cell death. Finally, the authors validate three RMB24 enhancers that are active in young hair cells and which have been previously shown to bind Pou4f3.

The experiments are well-executed and the data are clear. The results support the conclusions of the paper.

Much of the work in the paper has been reported before. The result that hair cell transcription factors operate in a network, with some transcription factors activating only a subset of hair cell genes, is an expected result. Since RMB24 is only one of many genes regulated directly by Pou4f3, it is not surprising that it cannot rescue the Pou4f3 knockout hair cell degeneration.

The identification of new hair cell enhancers may be of use to investigators wishing to express genes in hair cells.

In sum, this work, although carefully performed, does not shed significant new light on our understanding of hair cell development or survival.

Author Response

The following is the authors’ response to the original reviews.

Reviewer #1 (Recommendations For the Authors):

(1) While not absolutely necessary - it would be nice to see at least at the in-situ level what happens to the handful of other HC-important transcription factors in the Rbm24 KO (IKZF2, Barlh1, RFX) as the authors did look at Insm1.

Reply: Thanks for your suggested experiments. We agree that knowing whether the genes that are known to be involved in cell survival regulation are changed will provide insights into the mechanisms underlying cell death of Rbm24-/- HCs. Our data showed that Ikzf2 seemed to be upregulated when in the Rbm24-/- HCs, relative to Rbm24+/+ HCs at P5. We also tested Barlh1 and RFX, but we did not obtain confident data to present. Nonetheless, following the reviewer’s logic, we further tested Gata3, another gene involved in HC survival, and found that Gata3 was down-regulated in Rbm24 -/- HCs, compared to Rbm24+/+ HCs. Please refer to the text on lines 12-22 on page 12 and lines 1-10 on page 13, and Figure 3-figure supplement 1.

(2) Major comments: The nomenclature for mouse gene vs. mouse protein needs to be addressed throughout the manuscript. The nomenclature when referring to a mouse gene: gene symbols are italicized, with only the first letter in upper-case (e.g. Rbm24).

The nomenclature when referring to a mouse protein: Protein symbols are not italicized, and all letters are in upper-case (e.g. RBM24).

Reply: Thanks for pointing it out. In the entire manuscript, we have followed the reviewer’s comments to list gene and protein.

(3) Supplemental Figure 2D: Individual data points should be displayed on the bar graph via dots. SEM is not appropriate for this graph as SEM precision with only 3 samples is low. Furthermore, readers are more interested in knowing the variability within samples and not proximity of mean to the population mean, therefore standard deviation (SD) should be used instead.

Reply: We have edited the Figure 1-figure supplement 2D, as suggested. The Figure 1figure supplement 2 legend was updated, too. Please refer to line 21-22 on page 32.

(4) Red/Green should be avoided, especially when both are on the same image (merged immunofluorescence images that are found throughout the manuscript). I highly recommend changing to a color-blind friendly color scheme (such as cyan/green/magenta, cyan/magenta/yellow, etc.) for inclusivity.

Reply: Thanks for pointing it out. We have changed the red to magenta in all our Figures and figure supplements.

(5) Minor comments: As CRISPR-stop is a major method used throughout the paper, a brief explanation is needed for readers to understand what this methodology entails and why it was used. Something along the lines of," The CRISPR-stop technique allows for the introduction of early stop codons without the induction of DNA damage via Cas9 which can cause deleterious effects".

Reply: We have further elaborated how CRISPR-stop works and its advantages. Please refer to lines 8-13 on page 5.

(6) Page 5; line 5 - "Phenotypes occur earlier..." Grammar

Reply: The grammar error was corrected. Please refer to line 4, page 5.

(7) Page 5; line 5 - "Given Pou4f3 is the upstream regulator..." Not proven, rephrase

Reply: We have rephrased this sentence. Please refer to lines 5-6 on page 5.

(8) Supplemental 1A: Fine, Proof of knockout, I wouldn't mention INSM1 being "irregular"

Reply: We have rephrased this sentence. Please refer to lines 2-3 on page 6.

(9) Page 5; line21 - "Alignment of Insm1+ OHCs was not as regular..." Not a good description

Reply: We have rephrased this sentence. Please refer to lines 2-3 on page 6.

(10) Page 6; line11 - "Rbm24 was completely absent.." Redundancy with line 9

Reply: Thanks for pointing it out, and we have removed the redundant sentence.

(11) Page 7 - HA tag should be indicated originally as: Hemaglutinin (HA)

Reply: We have switched “HA” to “Hemaglutinin (HA)”. Please refer to line 15, page 7.

(12) Page 9, line 11- "Determine if autonomous/noncell autonomous." Disagree, cells still clustered in supplemental fig 4.

Reply: We have removed this sentence.

Reviewer #2 (Recommendations For The Authors):

The writing of the manuscript is adequate, but it would certainly be improved by professional editing.

Reply: Thanks for the reviewer’s encouraging comments. The revised version of our manuscript has been edited by an English native speaker.

Version 2

Abstract

Abstract

Mammals harbor a limited number of sound-receptor hair cells (HCs) that cannot be regenerated after damage. Thus, investigating the underlying molecular mechanisms that maintain HC survival is crucial for preventing hearing impairment. Intriguingly, Pou4f3-/- or Gfi1-/-HCs form initially but then rapidly degenerate, whereas Rbm24-/-HCs degenerate considerably later. However, the transcriptional cascades involving Pou4f3, Gfi1, and Rbm24 remains undescribed. Here, we demonstrate that Rbm24 expression is completely repressed in Pou4f3-/-HCs but unaltered in Gfi1-/- HCs, and further that the expression of both POU4F3 and GFI1 is intact in Rbm24-/- HCs. Moreover, by using in vivo mouse transgenic reporter assays, we identify three Rbm24 enhancers to which POU4F3 binds. Lastly, through in vivo genetic testing of whether Rbm24 restoration alleviates the degeneration of Pou4f3-/- HCs, we show that ectopic Rbm24 alone cannot prevent Pou4f3-/- HCs from degenerating. Collectively, our findings provide new molecular and genetic insights into how HC survival is regulated.

Introduction

Housed in the mammalian cochlea, the auditory epithelium—also known as the organ of Corti—contains the mechanosensory receptors hair cells (HCs) that detect sound information [1, 2]. Two types of HCs exist, the inner HCs (IHCs) and outer HCs (OHCs), and these appear in, respectively, a single row and three rows [3]. Both OHCs and IHCs are derived from cochlear progenitors expressing high levels of ATOH1, a master transcription factor (TF) in HC development [4-6, and no HCs form in the Atoh1-/-cochlea, highlighting the essential role of ATOH1 in specifying the general HC fate in the undifferentiated progenitors [7, 8]. Whereas OHCs uniquely express the motor protein PRESTIN (encoded by Slc26a5) and function as sound amplifiers [9, 10], IHCs specifically express FGF8, vGLUT3 (encoded by Slc17a8), and OTOFERLIN [11-15 and act as the primary sensory cells that form synapses with distinct subtypes of type I spiral (auditory) neurons [16-19. Moreover, INSM1 is necessary for stabilizing the OHC fate, and ∼50% of Insm1-/- OHCs tend to transdifferentiate into IHC-like cells [20, 21]; conversely, IKZF2 is not required in early OHC development but is essential for consolidating the OHC fate, and Ikzf2cello/cello mutant OHCs are dysfunctional and misexpress IHC genes [22]. INSM1 is an epistatic but indirect positive regulator of Ikzf2, and restoration of IKZF2 expression can partially mitigate the phenotypes of Insm1-/- OHCs [21]. In contrast to INSM1 and IKZF2, TBX2 is required in IHC fate specification, differentiation, and maintenance, and IHCs convert into OHCs in the absence of TBX2 [23-26.

The survival of cochlear HCs must be maintained after their production. POU4F3, a POU-domain family TF encoded by the hearing-loss gene DFNA15, is essential for HCs to survive [27-31. However, unlike ATOH1, POU4F3 is not involved in the fate determination of HCs [32]. As a target gene regulated by ATOH1 [28, 33], Pou4f3 is expressed in HCs between embryonic day 14.5 (E14.5) and E16 in a basal-to-apical gradient, and POU4F3 then activates the expression of Gfi1, which encodes a zinc-finger TF [34, 35]; Gfi1 is undetectable in Pou4f3-deficient HCs [35], and HCs, particularly OHCs, degenerate in Pou4f3 and Gfi1 mutants by birth [35]. Besides POU4F3 and Gfi1, the RNA-binding protein RBM24 is also specifically expressed in cochlear HCs [36]. We recently showed that RBM24 is indispensable for maintaining OHC survival, but the OHC death in Rbm24 mutants occurs considerably later than in Pou4f3 and Gfi1 mutants; OHCs develop normally until birth but most OHCs undergo cell death by postnatal day 19 (P19) in Rbm24-/- mice [37]. How Rbm24 expression is regulated during cochlear HC development is unknown.

The similar but delayed phenotype of OHC death in Rbm24 mutants relative to that in Pou4f3- and Gfi1-deficient mice prompted us to dissect the potential genetic interactions among them by using an in vivo genetic approach. Our results showed that the onset of RBM24 expression was completely repressed in Pou4f3-/- HCs, but that, unexpectedly, RBM24 expression was normal in Gfi1-/- HCs. Moreover, the expression of neither POU4F3 nor GFI1 was altered in Rbm24-/- HCs. Thus, POU4F3, but not GFI1, is required in Rbm24 expression. Furthermore, we identified three Rbm24 enhancers that were sufficient to drive specific EGFP reporter expression in HCs, and these enhancers are likely bound by POU4F3. Lastly, we found that restoration of RBM24 expression alone cannot alleviate the degeneration of Pou4f3-/- HCs, which indicates that the expression of additional POU4F3-targeted genes must be restored to enable Pou4f3-/- HCs to survive. Our study provides new insights into the genetic interactions among Pou4f3, Gfi1, and Rbm24, which hold potential applications in HC protection.

Results

RBM24 expression is completely repressed in Pou4f3-/- cochlear HCs

HC degeneration occurs in both Pou4f3-/- and Rbm24-/-mice, with the phenotype appearing earlier and being more severe in Pou4f3-/-mice [35, 37]. This led us to speculate that genetic interaction exists between Pou4f3 and Rbm24. We reasoned that if POU4F3 is an upstream positive regulator of Rbm24, RBM24 expression would be downregulated in the absence of POU4F3. To rapidly test this possibility, we exploited our previously established CRISPR-stop approach [38]. CRISPR-stop allows early stop codons to be introduced without inducing DNA damage through Cas9, which can cause deleterious effects [39]. More importantly, the CRISPR-stop approach can generate Founder 0 (F0) mice carrying homozygous or mosaic homozygous gene mutations, and the F0 mice are thus immediately ready for phenotypic analysis, considerably faster than in the case with traditional gene-targeting methods [37, 38]. Co-injecting one sgRNA (sgRNA-1) against Pou4f3 and base-editor components into one-cell-stage mouse zygotes yielded F0 mice, whose tail DNA was subject to Sanger sequencing (Figure 1-figure supplement 1A). Relative to wild-type (WT) mice (Figure 1-figure supplement 1B), the F0 mice with homozygous premature emergence of the stop codon TAG were defined as Pou4f3-/- mice and were immediately ready for phenotypic analysis (Figure 1-figure supplement 1C).

RBM24 expression is repressed in cochlear HCs in the absence of POU4F3.

(A) Simple illustration of how Pou4f3-/- strain was generated. (B) One example gel image of tail-DNA PCR used to distinguish WT (Pou4f3+/+), heterozygous (Pou4f3+/-), and homozygous (Pou4f3-/-) mice. (C-F’’’) Triple staining of RBM24, POU4F3, and BCL11B in WT (C and E-E’’’) and Pou4f3-/-(D and F-F’’’) mice (n=3 for each) at E16.5; only the RBM24 (green) channel (together with nuclear staining) is shown in (C and D) at low magnification. (E-E’’’) and (F-F’’’): High-magnification images of middle turn in WT and Pou4f3-/- mice, respectively. In the absence of POU4F3, RBM24 expression completely disappeared, although nascent BCL11B+ OHCs were present. OHC: outer hair cell; IHC: inner hair cell. Scale bars: 100 μm (D), 20 μm (F’’’).

Triple staining of POU4F3, RBM24, and INSM1 revealed that OHCs in WT mice at E16.5 were POU4F3+/RBM24+/INSM1+, whereas IHCs expressed POU4F3 and RBM24 but not INSM1 (Figure 1-figure supplement 1D-D’’’). Conversely, POU4F3 expression was absent in Pou4f3-/- mice (Figure 1-figure supplement 1E-E’’’), confirming that POU4F3 translation was blocked, and unlike in WT mice, RBM24 expression was undetectable in the Pou4f3-/- mice at E16.5 (Figure 1-figure supplement 1E-E’’’). Notably, INSM1 expression appeared normal in Pou4f3-/- mice (arrows in Figure 1-figure supplement 1E-E’’’). Moreover, the presence of INSM1+ OHCs in the Pou4f3-/- mice eliminated the possibility that the absence of RBM24 was due to a secondary effect of OHC death or delayed differentiation, and also agreed with previous reports that initial HC differentiation can occur without POU4F3 [32, 35]. Thus, the rapid Pou4f3 loss-of-function analysis by using CRISPR-stop supported our hypothesis that POU4F3 is required for turning on RBM24 expression.

To further validate the observation described above, we constructed germ-line-stable Pou4f3 mutants in which the entire Pou4f3 genomic region between sgRNA-2 and sgRNA-3 was deleted (Figure 1A). The three obtained genotypes, Pou4f3+/+, Pou4f3+/-, and Pou4f3-/-, were readily distinguished using tail-DNA PCR (Figure 1B). Relative to WT mice (Figure 1C), Pou4f3-/- mice again completely lacked RBM24 expression at E16.5 (Figure 1D). Similar to INSM1, BCL11B is an OHC marker [20], and triple staining of RBM24, POU4F3, and BCL11B revealed that as in WT HCs (Figure 1E-E’’’), BCL11B was normally expressed in OHCs lacking both POU4F3 and RBM24 at E16.5 (Figure 1F-F’’’). This result again confirmed that nascent OHCs were normally produced in the absence of POU4F3. Moreover, in contrast to WT mice at P1 (Figure 1-figure supplement 2A-A’’), the germline Pou4f3-/- mutants showed HC degeneration at P0 (Figure 1-figure supplement 2B-B’’) and P1 (Figure 1-figure supplement 2C-C’’). Normalizing the numbers of the remaining HCs in the Pou4f3-/-mice at P0 or P1 against those in WT mice at P1 revealed that in P0 Pou4f3-/- mice, 35.94% ± 4.52%, 38.16% ± 2.79%, and 63.8% ± 5.28% of the HCs survived in basal, middle, and apical cochlear turns, respectively, whereas in P1 Pou4f3-/- mice, 5.54% ± 3.11%, 15.79% ± 3.65%, and 65.64% ± 7.95% of the HCs survived. HC degeneration in the middle and basal turns, but not the apical turn, was significantly more severe at P1 than at P0 (Figure 1-figure supplement 2D). Lastly, unlike in WT cochleae in which all MYO7A+ HCs expressed RBM24 (Figure 1-figure supplement 2E-E’’), in Pou4f3-/- cochleae, the remaining HCs lacked RBM24 expression (arrows in Figure 1-figure supplement 2F-F’’). Collectively, our results obtained using two distinct Pou4f3-deficient models indicated that POU4F3 is indispensable for turning on RBM24 expression. However, whether GFI1 is also essential for RBM24 expression remained unknown.

Construction of Gfi1-3×HA-P2A-Cre/+ knockin mouse strain

We sought to determine whether POU4F3 regulates Rbm24 expression through GFI1 or independently of GFI1. Because a suitable commercial GFI1 antibody for immunostaining was unavailable, we constructed a knockin mouse strain, Gfi13×HA-P2A-Cre/+ (Gfi1HA-Cre/+ in brief), by using our routine CRISPR/Cas9 approach (Figure 2-figure supplement 1A-C); here, the GFI1 C-terminus was tagged with three Hemagglutinin (HA) fragments and Cre expression was under the control of endogenous cis-regulatory elements (CREs) of Gfi1. The obtained WT (Gfi1+/+), heterozygous (Gfi1HA-Cre/+), and homozygous (Gfi1HA-Cre/HA-Cre) mice were readily distinguished using tail-DNA PCR (Figure 2-figure supplement 1D). Southern blotting revealed that in addition to being inserted in the Gfi1 locus, the targeting vector (Figure 2-figure supplement 1B) was randomly inserted in an unknown genomic region; however, the random insertion likely occurred in a silent genomic region as indicated by the analysis discussed below.

GFI1 is dispensable for RBM24 expression.

(A) Simple cartoon depicting how Gfi1 was inactivated in one-cell-stage zygotes derived from male Gfi1HA-Cre/+ mice by using the CRISPR-stop approach. (B-C) Using sgRNA-6 as an example, Sanger sequencing chromatograms of control Gfi1HA-Cre/+ (B) and F0 Gfi1-/- (C) samples are presented. The base “C” (black arrow in B) was converted to “T” (red arrow in C), resulting in pre-emergence of the translation stop codon TAG. The red “T” appears as a single peak, indicating that the stop codon pre-emerged in both alleles. (D-E’’) Dual staining of HA (GFI1) and RBM24 in cochleae from control Gfi1HA-Cre/+(D-D’’, n=3) and F0 Gfi1-/- (E-E’’) mice (n=4) at E16.5. RBM24 expression (E’) was not altered in the absence of HA (GFI1) expression (E). OHC: outer hair cell; IHC: inner hair cell. Scale bar: 20 μm (E’’).

Dual staining of HA (GFI1) and the pan-HC marker MYO7A revealed that, similar to Gfi1+/+ mice (Figure 2-figure supplement 1E-E’’), Gfi1HA-Cre/HA-Cremice showed normal HC development at P1 (Figure 2-figure supplement 1F-F’’). Moreover, HA (GFI1) was highly expressed in all MYO7A+ IHCs and OHCs in Gfi1HA-Cre/HA-Cre mice (arrows in Figure 2-figure supplement 1F-F’’). This finding confirmed that Gfi1 endogenous expression is unaffected in Gfi1HA-Cre/HA-Cremice, which represents an advantage over the previous Gfi1Cre/+strain in which one copy of Gfi1 is lost and early onset of hearing loss occurs [40, 41].

We also performed fate-mapping analysis in Gfi1HA-Cre/+; Rosa26-loxp-stop-loxp-tdTomato (Ai9)/+ (Gfi1HA-Cre/+; Ai9/+) mice at P2. The Gfi1HA-Cre/+; Ai9/+ model allowed us to both visualize the temporal GFI1 protein-expression pattern and permanently mark cells expressing Gfi1 by using tdTomato. Neither tdTomato nor HA was detected in the MYO7A+ HCs of control Ai9/+ mice (Figure 2-figure supplement 1G-G’’’ and I-I’’), whereas the majority of MYO7A+ HCs expressed tdTomato and HA in the Gfi1HA-Cre/+; Ai9/+ mice (Figure 2-figure supplement 1H-H’’’ and J-J’’). HA (GFI1) was generally expressed more highly in IHCs than OHCs (Figure 2-figure supplement 1J-J’’), and the HA (GFI1) expression level exhibited manifest heterogeneity among the OHCs. We identified the OHCs expressing the highest (#1), intermediate (#2), and lowest (#3) levels of HA (GFI1) (arrows in Figure 2-figure supplement 1J-J’’), and we observed that, notably, such heterogenous GFI1 expression in neonatal HCs was not detected in Gfi1HA-Cre/HA-Cremice (Figure 2-figure supplement 1F-F’’), likely due to the higher level of HA-tagged GFI1 in Gfi1HA-Cre/HA-Cre than Gfi1HA-Cre/+mice. Besides the tdTomato+ HCs, we detected tdTomato+ cells in nonsensory regions (arrows in Figure 2-figure supplement 1H), consistent with a previous report [40]. Collectively, these results indicated that the Gfi1HA-Cre/+strain was suitable for visualizing GFI1 protein by using an anti-HA antibody, although random insertion of the targeting vector also exists here. Alternatively, Gfi1HA-Cre/+can at least be treated as a pseudo-transgenic mouse strain that can be used to reliably visualize GFI1 and trace cells expressing Gfi1.

GFI1 expression is prevented in Pou4f3-/- cochlear HCs

Because HA faithfully represented GFI1 expression in the Gfi1HA-Cre/+ strain, we expected to observe repression of HA expression in Pou4f3-/- HCs, as reported previously [34, 35]. We confirmed this by using our CRISPR-stop approach [38]. The experimental pipeline was mostly identical to that used for producing the Pou4f3 mutants (Figure 1-figure supplement 1), except that the zygotes here were derived from male Gfi1HA-Cre/+mice (Figure 2-figure supplement 2A). We obtained mosaic (or chimeric) Pou4f3-/- mice, as confirmed through Sanger sequencing of tail-DNA PCR samples (Figure 2-figure supplement 2B and C), partly because the injection time was the late stage of the one-cell-stage zygotes. In control Gfi1HA-Cre/+mice, a pure “C” base was present (blue arrow in Figure 2-figure supplement 2B), but a mixture of “C” and “T” double peaks existed in Gfi1HA-Cre/+; Pou4f3-/- (mosaic) mice (red arrow in Figure 2-figure supplement 2C).

In control Gfi1HA-Cre/+ mice at E16.5, all HCs expressed POU4F3, RBM24, and HA (GFI1), although the HA (GFI1) levels again appeared heterogenous among the OHCs (Figure 2-figure supplement 2D-D’’’). By contrast, in the Gfi1HA-Cre/+; Pou4f3-/- (mosaic) mice, we detected HCs that had either lost or maintained POU4F3 expression (Figure 2-figure supplement 2E-E’’’). Notably, POU4F3+ HCs expressed HA (GFI1) and RBM24 (blue arrows in Figure 2-figure supplement 2E-E’’’), whereas both HA (GFI1) and RBM24 were absent in HCs that had lost POU4F3 expression (orange arrows in Figure 2-figure supplement 2E-E’’’). This again confirmed that HA is a reliable readout for GFI1 expression and that the expression is sensitive to the loss of POU4F3. Moreover, the results supported the view that POU4F3 regulates Rbm24 in a cell-autonomous manner.

GFI1 is dispensable for RBM24 expression

Next, we produced Gfi1-/- mutants by using the same CRISPR-stop approach [38]. One-cell-stage zygotes derived from male Gfi1HA-Cre/+mice were injected with base-editor components and four different sgRNAs located in distinct exons of Gfi1 (Figure 2A). The reason for the combined use of four sgRNAs is detailed in the discussion section. With sgRNA-6, for example, Sanger sequencing of tail DNA revealed that relative to control Gfi1HA-Cre/+mice (black arrow in Figure 2B), F0 mice showed premature emergence of the TAG stop codon, which resulted in homozygous Gfi1 inactivation (red arrow in Figure 2C). All HCs expressed HA (GFI1) and RBM24 in control Gfi1HA-Cre/+ mice (Figure 2D-D’’), and, notably, RBM24 expression was maintained in Gfi1-/- HCs, which showed no HA (GFI1) expression at E16.5 (Figure 2E-E’’). This finding suggested that RBM24 expression does not depend on GFI1.

The advantage of this Gfi1-/- model is that it allows rapid and direct confirmation of the absence of GFI1 expression in F0 mice. However, complete loss of GFI1 expression in all HCs cannot be guaranteed here at single-cell resolution through HA staining, because only one allele of Gfi1 was Gfi1HA-Cre. Thus, to eliminate the possibility that only the HA-tagged Gfi1 allele was mutated, we generated germ-line-stable Gfi1 mutants in which the majority of the Gfi1 DNA fragment between sgRNA-4 and sgRNA-9 was deleted (Figure 2-figure supplement 3A). The WT (Gfi1+/+), Gfi1+/-, and Gfi1-/- mice were readily identified using tail-DNA PCR (Figure 2-figure supplement 3B). In agreement with previous findings [42], dual staining of RBM24 and POU4F3 revealed that relative to WT mice (Figure 2-figure supplement 3C-C’’), Gfi1-/- mice (Figure 2-figure supplement 3D-D’’) showed severe degeneration of HCs at P1, particularly OHCs; this validated the successful generation of the Gfi1-/- mice. Notably, the surviving POU4F3+ HCs maintained the expression of RBM24 (orange arrows in Figure 2-figure supplement 3D-D’’). By contrast, we observed no significant difference between WT and Gfi1-/- mice at E16.5: both WT and Gfi1-/- HCs expressed POU4F3 and RBM24, and both WT and Gfi1-/- OHCs expressed BCL11B (Figure 2-figure supplement 3E-F’’’). This suggests that the degeneration of Gfi1-/- HCs does not begin by E16.5. The presence of POU4F3 in Gfi1-/- HCs agreed with the previously mentioned notion that Pou4f3 is epistatic to Gfi1. Collectively, the results of analyses of both Gfi1 mutant models support the conclusion that GFI1 is dispensable for RBM24 expression.

POU4F3 and GFI1 expressions are normal in Rbm24-/- cochlear HCs

Considering that POU4F3 is upstream and a positive regulator of Rbm24, we predicted that POU4F3 expression would be unaffected in Rbm24-/- HCs. To test this, we established an Rbm24-/- mouse strain by injecting one Rbm24 sgRNA (sgRNA-10) into one-cell-stage zygotes derived from male Gfi1HA-Cre/+ mice (Figure 3A). We selected Gfi1HA-Cre/+ zygotes in order to concurrently assess GFI1 and POU4F3 expression patterns in Rbm24-/- HCs. Relative to control Gfi1HA-Cre/+; Rbm24+/+ mice (Figure 3B), Gfi1HA-Cre/+; Rbm24-/- (mosaic) mice (Figure 3C) showed premature emergence of the TAG stop codon. Notably, Sanger sequencing of tail DNA revealed that the Rbm24 mutation was mosaic, because mixed “T” and “C” peaks existed (red arrow in Figure 3C).

POU4F3 and GFI1 expressions are normal in the absence of Rbm24.

(A) Simple cartoon showing how CRISPR-stop was used to induce mosaic inactivation of RBM24 in one-cell-stage mouse zygotes harboring Gfi1HA-Cre/+. Notably, the injection was in the late one-cell stage of the zygotes, which resulted in high rates of final mosaic inactivation. (B-C) Sanger sequencing chromatograms of control Gfi1HA-Cre/+; Rbm24+/+ (B) and Gfi1HA-Cre/+; Rbm24-/- (mosaic) (C) samples. The base “C” (black arrow in B) was converted to “T” (red arrow in C) in a fraction of cochlear cells. Mosaic inactivation of Rbm24 is evidenced by the double peaks of “T” and “C” (red arrow in C). (D-E’’’) Triple staining of RBM24, HA, and Pou4f3 in cochlear samples (basal turns) of control Gfi1HA-Cre/+; Rbm24+/+(D-D’’’, n=3) and Gfi1HA-Cre/+; Rbm24-/- (mosaic) (E-E’’’, n=3) mice at E17. Consistent with the Sanger sequencing results (C), RBM24 expression was found to be inactivated in cochlear HCs in a mosaic pattern (E). Orange arrows in (E-E’’’): one OHC that lost RBM24 expression; blue arrows in (E-E’’’): one OHC that maintained RBM24 expression. Regardless of whether RBM24 expression was inactivated or not, the expression of HA (GFI1) and POU4F3 was unaltered. OHC: outer hair cell; IHC: inner hair cell. Scale bar: 20 μm (E’’’).

The mosaic inactivation of RBM24 was further confirmed through triple staining of RBM24, HA, and POU4F3 (Figure 3D-E’’’). Relative to the expression in control Gfi1HA-Cre/+; Rbm24+/+ mice (Figure 3D-D’’’), RBM24 expression disappeared in a fraction of cochlear HCs (orange arrows in Figure 3E-E’’’) but remained normal in other HCs (blue arrows in Figure 3E-E’’’) of the Gfi1HA-Cre/+; Rbm24-/- (mosaic) mice at E17. Notably, regardless of whether RBM24 expression was inactivated or not in the cochlear HCs, the expression patterns of both HA (GFI1) and POU4F3 remained intact. This suggests that Pou4f3 is epistatic to Rbm24 and that inactivation of the Rbm24 gene does not affect POU4F3 expression. Moreover, our results suggested that Gfi1 and Rbm24 do not interact genetically: Gfi1 inactivation did not affect Rbm24 expression (Figure 2 and Figure 2-figure supplement 3), and vice versa (Figure 3E-E’’’).

GATA3 is downregulated and IKZF2 is upregulated in Rbm24-deficient HCs

We next determined whether the expression patterns of two additional genes, Gata3 and Ikzf2, which are involved in OHC development and survival [21-23, 43, 44], were altered in the absence of RBM24. For analyzing GATA3, mosaic Rbm24 mutant mice were produced using the CRISPR-stop approach (Figure 3-figure supplement 1A). Dual immunostaining of GATA3 and RBM24 revealed that GATA3 was evenly expressed in control OHCs and IHCs at P1 (Figure 3-figure supplement 1B-B’’). By contrast, the GATA3 level in OHCs lacking RBM24 expression (white arrows in Figure 3-figure supplement 1C-C’’) was manifestly weaker than that in neighboring OHCs that retained RBM24 expression (yellow arrows in Figure 3-figure supplement 1C-C’’). This result suggests that GATA3 is downregulated in Rbm24-deficient OHCs. OHCs degenerate in Gata3+/- mice [43], and thus the downregulation of GATA3 might contribute to the cell death of Rbm24-deficient OHCs.

For analyzing IKZF2, mosaic Rbm24 mutant mice were produced using zygotes obtained by breeding male Ikzf2V5/+ mice with WT female mice (Figure 3-figure supplement 1D). Notably, the C-terminus of IKZF2 here was fused with three V5 tags to allow IKZF2 protein to be visualized using a V5 antibody [21, 23]. In control Ikzf2V5/+; Rbm24+/+ mice, V5 (IKZF2) was evenly distributed in OHCs at P5 (Figure 3-figure supplement 1E-E’’). By contrast, in the mosaic Ikzf2V5/+; Rbm24-/-mice, the V5 signal in the OHCs that had lost RBM24 expression (yellow arrows in Figure 3-figure supplement 1F-F’’) was unfailingly higher than the nearby OHCs expressing RBM24 (white arrows in Figure 3-figure supplement 1F-F’’). It supports that RBM24 directly or indirectly represses the IKZF2 expression.

Three Rbm24 enhancers can drive specific EGFP expression in cochlear HCs

After showing that POU4F3, but not GFI1, is indispensable in mediating Rbm24 expression, we determined the mechanism by which POU4F3 controls Rbm24 expression, particularly the role of the CREs of Rbm24. According to our previous high-throughput ATAC-seq (transposase-accessible chromatin sequencing) analysis of neonatal cochlear HCs [8], four CREs of Rbm24 were identified: one proximal promoter (arrow in Figure 4A), and three distal potential enhancers that were defined as Eh1, Eh2, and Eh3 (dotted boxes in Figure 4A). Eh1 and Eh2 were located upstream and Eh3 was downstream of the Rbm24 coding region. Moreover, we reanalyzed the results of POU4F3 Cut&Run assays from one previous study [33], and we found that POU4F3 binds to Eh1, Eh2, and Eh3 but not the Rbm24 promoter (Figure 4A).

Three Rbm24 enhancers are sufficient to drive specific EGFP expression in cochlear HCs.

(A) isualization of ATAC-seq (top row, orange) of P1 cochlear HCs (from our previous study, GSE181311) and POU4F3 Cut&Run assay (bottom row, blue) of E17.5 cochlear HCs (from another study, GSE150391) by using Integrative Genomics Viewer. Black arrow: Rbm24 promoter; dotted boxes: three Rbm24 enhancers (Eh1, Eh2, and Eh3). (B-G’’) Dual labeling for EGFP and MYO7A in Eh1-EGFP+ (B-C’’, n=7), Eh2-EGFP+ (D-E’’, n=6), and Eh3-EGFP+ (F-G’’, n=4) mice at P1. Only the EGFP channel (plus nuclear staining) is shown for whole-mount samples (B, D, F). In cryosection cochlear samples, EGFP labeling overlapped with HC marker MYO7A. OHCs: outer hair cells; IHC: inner hair cell; HC: hair cell. Scale bars: 100 μm (F), 20 μm (G’’).

Whether Eh1, Eh2, and Eh3 are bona-fide Rbm24 enhancers has remained unknown. We reasoned that if Eh1, Eh2, and Eh3 were Rbm24 enhancers, one of these, together with the mini-promoter of mouse heat shock protein 68 gene (Hsp68) [8, 45-47], would be sufficient to drive specific reporter expression in cochlear HCs, and to test this, we established three transgenic mouse strains: Eh1-EGFP+ (Figure 4B-C’’), Eh2-EGFP+ (Figure 4D-E’’), and Eh3-EGFP+ (Figure 4F-G’’); in these strains, EGFP expression would be driven by the mini-promoter of Hsp68 and Eh1 or Eh2 or Eh3, respectively. The mini-promoter of Hsp68 alone is reported to be incapable of driving EGFP expression [48], and in contrast to this, we detected strong EGFP expression through whole-mount analysis in all three transgenic lines (Figure 4B, D and F). Moreover, dual labeling for EGFP and MYO7A in cryosectioned cochleae showed that EGFP was specifically expressed in IHCs and OHCs in all three strains at P1 (Figure 4C-C’’, E-E’’ and G-G’’). Collectively, our transgenic assay results suggest that Eh1, Eh2, and Eh3 are Rbm24 enhancers, and further that POU4F3 regulates Rbm24 expression primarily by binding to the Rbm24 enhancers.

Forced RBM24 expression fails to alleviate the degeneration of Pou4f3-/- HCs

Our results thus far clearly showed that POU4F3 can regulate Rbm24 expression, but whether ectopic RBM24 expression can alleviate the degeneration of Pou4f3-/- HCs remained unknown. Thus, we first established a new conditional mouse model, Rosa26loxp-stop-loxp-Rbm24*3×HA/+(Rosa26Rbm24/+ in short) (Figure 5A and B), and to turn on ectopic RBM24 expression in cochlear HCs, we further crossed the Rosa26Rbm24/+strain with the strain Atoh1Cre/+, which targets a majority of cochlear HCs and a fraction of supporting cells (SCs) [49]. Notably, in the Rosa26Rbm24/+ strain, RBM24 was tagged with three HA fragments, which allowed endogenous and ectopic RBM24 to be distinguished. In control Pou4f3+/+ mice (Figure 5C-C’’) and germ-line-stable Pou4f3-/- mice (Figure 5D-D’’), MYO7A+ HCs did not express HA (RBM24), whereas almost all MYO7A+ HCs expressed HA (RBM24) in Pou4f3+/+; Atoh1Cre/+; Rosa26Rbm24/+ mice at P1 (white arrows in Figure 5E-E’’). As expected, besides HCs, we detected a few SCs expressing HA (RBM24) but not MYO7A (orange arrows in Figure 5E-E’’). The cochlear HCs expressing HA (RBM24) appeared normal, suggesting that the cells can tolerate the additional RBM24 expression by P1. Collectively, these results supported the conclusions that the Rosa26Rbm24/+ model was successfully generated and that ectopic RBM24 was expressed in cochlear HCs in Pou4f3+/+; Atoh1Cre/+; Rosa26Rbm24/+ mice.

Forced expression of RBM24 fails to rescue OHC degeneration in Pou4f3-/-mutants.

(A) Generation of Rosa26loxp-stop-loxp-Rbm24*3×HA/+ (Rosa26Rbm24/+) mouse strain. The C-terminus of ectopic Rbm24 was fused with three HA tags. (B) One example gel image of tail-DNA PCR used to distinguish WT (+/+) and knockin (Rosa26Rbm24/+) mice. (C-F’’) Dual staining of HA (RBM24) and HC marker MYO7A in mice featuring four distinct genotypes at P1: Pou4f3+/+ (C-C’’, n=3), Pou4f3-/- (D-D’’, n=3), Pou4f3+/+; Atoh1Cre/+; Rosa26Rbm24/+ (E-E’’, n=3), and Pou4f3-/-; Atoh1Cre/+; Rosa26Rbm24/+ (F-F’’, n=3). Ectopic HA (RBM24) was not detected in Pou4f3+/+ (C) and Pou4f3-/- (D) mice, but was detected in both Pou4f3+/+; Atoh1Cre/+; Rosa26Rbm24/+(E) and Pou4f3-/-; Atoh1Cre/+; Rosa26Rbm24/+(F) mice. White arrows in (E-E’’): one MYO7A+ IHC that expressed ectopic HA (RBM24). HCs appeared normal by P1, despite the induction of ectopic RBM24 expression. Orange arrows in (E-E’’): one SC that expressed HA (RBM24) but not MYO7A. White arrows in (F-F’’): one remaining MYO7A+ HC that expressed ectopic RBM24. Overall, many of the Pou4f3-/- HCs degenerated even though ectopic RBM24 expression was induced. OHC: outer hair cell; IHC: inner hair cell; HC: hair cell. Scale bar: 20 μm (F’’).

In contrast to our expectation, ectopic RBM24 expression failed to mitigate the degeneration of Pou4f3-/- HCs. Severe degeneration of HCs (both IHCs and OHCs) occurred in Pou4f3-/-; Atoh1Cre/+; Rosa26Rbm24/+mice (Figure 5F-F’’) and was indistinguishable from that in Pou4f3-/- mice (Figure 5D-D’’), except that the surviving HCs expressed RBM24 in the Pou4f3-/-; Atoh1Cre/+; Rosa26Rbm24/+ mice (arrows in Figure 5F-F’’). This result suggests that restoration of RBM24 expression alone is not sufficient to prevent Pou4f3-/- cochlear HCs from undergoing degeneration.

Discussion

Molecular mechanisms underlying cochlear HC survival

Mammalian sound-receptor HCs are vulnerable to various genetic mutations, environmental ototoxic factors, and aging. HC degeneration is one of the primary reasons for human sensorineural hearing impairment [50], and several genes whose mutations lead to HC degeneration starting at different ages have been identified previously. For example, HC development is severely defective in Atoh1-/- mutants [7, 51], and Atoh1-/- cochlear sensory cells undergo apoptosis. However, whether the absence of HCs in Atoh1-/-mice is because of HCs not being produced or dying immediately after initial emergence remains unclear, partly due to the difficulty of unambiguously defining nascent HCs by using molecular markers.

Unlike in Atoh1-/- mutants, in both Pou4f3-/-and Gfi1-/- mice [32, 34, 35], initial cochlear HC development is normal but becomes defective at perinatal ages, consistent with the notion that POU4F3 and GFI1 are dispensable for HC fate specification but necessary for subsequent differentiation and survival. Intriguingly, caspase-3 is active during HC death in Pou4f3-/- mutants, and the antiapoptotic factor z-VAD-fmk exerts a protective effect on Pou4f3-/-HCs between E14.5 and E16.5 [52]. Moreover, we noted here milder overall HC degeneration in Gfi1-/- mice than in Pou4f3-/- mice at P1, because only OHC degeneration occurred in Gfi1-/- mice but both IHCs and OHCs were degenerated in Pou4f3-/- mice (Figure 1-figure supplement 2 and Figure 2-figure supplement 3).

Gfi1 is a recognized target of POU4F3 [35], but whether forced GFI1 expression can alleviate the degeneration of Pou4f3-/-HCs is unknown. Similarly, Pou4f3 is one of the target genes regulated by ATOH1 [33], but whether forced expression of POU4F3 or GFI1, or both, can mitigate the developmental defects of Atoh1-/- HCs remains undetermined. Future studies must address these questions to enable comprehensive understanding of the mechanisms underlying the maintenance of cochlear HC survival.

Roles of RBM24 and its regulation during cochlear HC development

Shortly after cochlear HCs emerge, RBM24 expression begins and then is maintained permanently, as revealed by transcriptomic analyses and antibody staining [23, 36, 44, 53, 54]. RBM24 is not necessary in the early phase of cochlear HC development, because Rbm24-/- HC development is normal by P1, but RBM24 is required for OHC survival after birth [37]; Rbm24-/-OHCs, but not IHCs, are degenerated by P19 [37]. RBM24 is also involved in mRNA stability and pre-mRNA alternative splicing of several genes, including Cdh23 and Pcdh15, which are crucial for the development of HC stereocilia [55-57. Our study also revealed that GATA3 expression is decreased and IKZF2 expression is increased in OHCs in the absence of RBM24, which could be a direct or indirect effect of RBM24 loss. Nonetheless, single-cell transcriptomic analysis has not yet been performed on Rbm24-/- IHCs or OHCs, and future investigation is necessary to clarify the detailed molecular mechanism underlying Rbm24-/- HC degeneration.

What are the trans-acting factors involved in regulating Rbm24 expression? First, this study has provided strong genetic evidence indicating that POU4F3 is necessary for turning on Rbm24 expression; in the absence of POU4F3, Rbm24 expression was not triggered. Moreover, the normal expression of POU4F3 in Rbm24-/- HCs confirmed that Pou4f3 is epistatic to Rbm24 and that RBM24 is dispensable for Pou4f3 expression. Besides POU4F3, ATOH1 appears to regulate Rbm24 expression, as per two lines of evidence: one, RBM24 expression is lost in Atoh1-/- cochlear HCs [58]; and two, Rbm24 is one of the ATOH1 binding targets revealed by the ATOH1 Cut&Run assay [8, 33]. Notably, ATOH1 binds to both the Rbm24 promoter and the three Rbm24 enhancers (Eh1, Eh2, and Eh3) [8, 33], whereas POU4F3 only binds to the Rbm24 enhancers (Figure 4). Thus, POU4F3 and ATOH1 likely cooperate to regulate Rbm24 expression, and either Pou4f3 or Atoh1 mutation leads to repression of Rbm24 expression. Future conditional Pou4f3 loss-of-function studies are necessary to determine whether Rbm24 expression in adult HCs requires POU4F3.

Gfi1 and Rbm24 are expressed independently of each other

We initially hypothesized that POU4F3 regulates Rbm24 expression through GFI1. However, this hypothesis was not supported by our observation that RBM24 expression is normal in Gfi1-/- HCs (Figure 2 and Figure 2-figure supplement 3). Moreover, in the absence of RBM24, GFI1 expression was not altered in cochlear HCs. Thus, Rbm24 expression and Gfi1 expression appear to be independent of each other. This might be due to the functional difference between POU4F3 and GFI1 during cochlear HC development. Although both POU4F3 and GFI1 are necessary for promoting the expression of genes involved in HC differentiation [29, 31, 35, 42], GFI1, but not POU4F3, also represses the preceding expression of neural genes in nascent HCs [42].

Another observation here relevant to Gfi1 isoforms is noteworthy. We showed previously that one efficient sgRNA is adequate for inducing homozygous gene inactivation by using CRISPR-stop [37]. Here, we used four Gfi1 sgRNAs distributed across distinct exons (Figure 2A). Interestingly, we successfully established one Gfi1 mutant by using sgRNA-5 alone, and this, in principle, should effectively pre-stop GFI1 translation in exon 1, which codes for the SNAG repressor domain; the obtained Gfi1 mutant presented the HC degeneration phenotype, although HA (GFI1) remained detectable in HCs. This agrees with the notion that the Gfi1 mutant lacking the SNAG domain is equivalent to the Gfi1-null model [59]. Thus, Gfi1 is likely expressed as multiple unknown isoforms, many of which might be recognized by the HA-tag antibody because HA is tagged to the last exon (exon 6). However, when we used the four Gfi1 sgRNAs together, we were able to both reproduce the HC degeneration phenotype and completely block HA (GFI1) expression.

Why does ectopic RBM24 fail to alleviate the degeneration of Pou4f3-/- HCs?

Upon confirming the epistatic genetic interaction between Pou4f3 and Rbm24, we predicted that ectopic RBM24 expression should be able to, at least partly, alleviate the degeneration of Pou4f3-/- HCs, similar to what we recently reported in our study on INSM1 and IKZF2 in cochlear OHCs [21]. However, RBM24 failed to rescue the HC degeneration in Pou4f3-/- mice. Two potential explanations for this finding are the following: One, although Rbm24 expression is modulated by POU4F3, RBM24 is not directly involved in the pathway regulating HC survival; accordingly, cell death occurs later in Rbm24-/-HCs than in Pou4f3-/- HCs. Two, Rbm24 is a key POU4F3 downstream target, but forced expression of RBM24 alone cannot compensate for the loss of POU4F3 or other known POU4F3 targets such as orphan thyroid nuclear receptor Nr2f2 and Caprin-1 [60, 61]; CAPRIN-1 is recruited to stress granules in cochlear HCs exposed to ototoxic trauma [61].

Potential application of the three Rbm24 enhancers in cochlear HC gene therapy

Gene therapy is a promising strategy for restoring hearing capacity in humans with inherited gene mutations causing hearing impairment [50], and a few such therapy examples have been reported to date, including Otoferlin and vGlut3 gene-replacement therapies [62-65. Currently, therapeutic cDNAs are primarily delivered into HCs by using an adeno-associated virus (AAV) vector. Although several AAVs have been reported [66, 67], the vectors transfect cochlear cells non-selectively and HC-specific AAVs are not yet available. A solution to this problem is the following: instead of the CAG/CMV ubiquitous promoter widely used in current AAVs [68, 69], using any one of the three Rbm24 enhancers together with the Hsp68 mini-promoter (in brief Rbm24-Hsp68) should generate an AAV that would allow HC-specific transfection. Moreover, Rbm24 is permanently expressed in cochlear HCs, and if Rbm24-Hsp68 AAV acts as expected, it would represent a powerful tool for future HC-specific gene therapy at all postnatal ages, with potential applications in treating clinical human deafness.

Methods and materials

Mice

The Atoh1Cre/+ model was kindly provided by Dr. Lin Gan (Augusta University, USA). The Rosa26-loxp-stop-loxp-tdTomato (Ai9)/+ strain (Jax#: 007905) was from The Jackson Laboratory. The Ikzf2V5/+mouse strain is described in detail in our previous reports [21, 23]. All mice were bred and raised in an SPF-level animal room and all animal procedures were performed according to the guidelines (NA-032-2022) of the IACUC of the Institute of Neuroscience (ION), Center for Excellence in Brain Science and Intelligence Technology, Chinese Academy of Sciences.

One-step generation of homozygous Pou4f3, Gfi1, or Rbm24 mutants by using CRISPR-stop

The detailed protocol for using CRISPR-stop to generate homozygous gene mutants is described in our previous reports [37, 38]. Briefly, efficient pre-tested sgRNAs (Table S1) and hA3ABE3 were co-injected into one-cell-stage mouse zygotes that were then transplanted into pseudopregnant female mice, which gave birth to F0 mice. The F0 mice carrying the expected homozygous mutation (pre-emergence of protein translation stop codon) were identified using Sanger sequencing of tail-DNA PCR samples and were immediately ready for analysis.

Generating Pou4f3- or Gfi1-null mutants harboring large DNA fragment deletions by using CRISPR/Cas9

To construct germ-line-stable null mutants of either Pou4f3 or Gfi1, Cas9 mRNA, two efficient pre-tested sgRNAs located at the proximal and distal ends of the targeted gene, and a single-stranded DNA donor (120 bp) (Table S3) were co-injected into one-cell-stage WT zygotes. Notably, the left and right halves (60 bp each) of the single-stranded DNA donor were homologous to the 5ʹ and 3ʹ ends of the targeted gene, respectively. The post-injected zygotes were transplanted into pseudopregnant females, which gave birth to F0 mice; the F0 mice were subject to tail-DNA PCR screening with the primers listed in Table S2, and the mice harboring the designed large DNA deletion between the two sgRNAs were identified and further bred with WT mice to establish the germ-line-stable mutants (F1 or afterward).

Construction of Gfi13◊HA-P2A-Cre knockin mouse strain

An sgRNA against Gfi1 (5ʹ-ATGGACTCAAATGAGTACCC-3ʹ), Cas9 mRNA, and the targeting vector (Figure 2-figure supplement 1B) were co-injected into one-cell-stage WT mouse zygotes. The targeting vector comprised three portions: the 5ʹ homologous arm (800 bp), the 3ʹ homologous arm (800 bp), and the region between the 5ʹ and 3ʹ arms that contained three HA fragments followed by 2A-Cre. The F0 mice with the potential gene targeting (Figure 2-figure supplement 1C) were screened using tail-DNA PCR and then crossed with WT mice to produce F1 mice; these F1 mice were confirmed using tail-DNA PCR again and further screened using Southern blotting. The detailed Southern blotting protocol is described in our previous report [70]. Tail-DNA PCR was used for routine genotyping, and the knockin (Gfi1HA-Cre/+) and WT alleles were distinguished using the primers F4, R5, and R6 (Table S2).

Construction of Eh1-EGFP+, Eh2-EGFP+, and Eh3-EGFP+ transgenic reporter lines

The three transgenic reporter mouse lines used here, Eh1-EGFP+, Eh2-EGFP+, and Eh3-EGFP+, were produced using the same procedures. The core DNA sequences of each enhancer (Eh1, Eh2, or Eh3 in Figure 4A), the mRNA encoding PiggyBac transposase, and the PiggyBac vector (Figure 4B, D and F) were co-injected into one-cell-stage WT mouse zygotes. The PiggyBac vector contained the Eh1/Eh2/Eh3 core DNA sequence (Table S3), the mini-promoter of mouse Hsp68, and the EGFP coding sequence, and the vector was randomly integrated into the mouse genome by the transposase. The F0 mice harboring the PiggyBac vector were screened using tail-DNA PCR and further bred with WT mice to produce germ-line-stable F1 transgenic reporter strains. The samples analyzed in Figure 4B-G’’ were from F1 or later generations. The primers used for genotyping transgenic reporter strains were F8, F9, F10, and the common primer R11 (primer sequences are listed in Table S2).

Generation of Rosa26CAG-lsl-Rbm24*3×HA/+ mouse model

The Rosa26CAG-lsl-Rbm24*3×HA/+ (Rosa26Rbm24/+) knockin mouse strain was constructed through homologous recombination mediated by CRISPR/Cas9. A pre-tested Rosa26 sgRNA (5ʹ-ACTCCAGTCTTTCTAGAAGA-3ʹ), the targeting vector (Figure 5A), and Cas9 mRNA were co-injected into one-cell-stage WT mouse zygotes, and similarly as in other cases, F0 mice with potentially correct gene targeting were screened using tail-DNA PCR and further bred with WT mice to establish germ-line-stable F1 mice. The WT and knockin (Rosa26Rbm24/+) alleles were distinguished using the primers F12, R13, and R14 (Table S2).

Sample processing and immunofluorescence assay

Inner ears were dissected out and fixed in 4% paraformaldehyde (PFA) in PBS (E607016-0500, Sangon Biotech) at 4℃ overnight. For obtaining cochlear cryosections, inner ears were dehydrated in 30% sucrose (V900116, Sigma) at 4℃ before embedding into optimal cutting temperature (OCT) compound (4583, SAKURA), and then slices were cut at 14 μm thickness. The detailed protocol for immunofluorescence staining is described in our previous report [71]. The following primary antibodies were used: anti-RBM24 (rabbit, 1:500, 18178-1-AP, Proteintech), anti-POU4F3 (mouse, 1:500, sc-81980, Santa Cruz), anti-POU4F3 (rabbit, 1:500, NBP1-88349, Novus Biologicals), anti-HA (rat, 1:500, 11867423001, Roche), anti-MYO7A (rabbit, 1:500, 25-6790, Proteus Biosciences), anti-MYO7A (mouse, 1:500, MYO7A 138-1, Developmental Studies Hybridoma Bank), anti-CTIP2 (BCL11B) (rat, 1:500, ab18465, Abcam), anti-INSM1 (guinea pig, 1:6000, a kind gift from Dr. Carmen Birchmeier from Max Delbrueck Center for Molecular Medicine, Germany), anti-GFP (chicken, 1:500, ab13970, Abcam), anti-GATA3 (goat, 1:500, AF2605, R&D Systems), and anti-V5 (mouse, 1:500, MCA1360, Bio-Rad). Various corresponding Alexa Fluor-conjugated secondary antibodies were used for detecting the primary antibodies, and Hoechst 33342 (1:1000, H3570, Thermo Fisher Scientific) was used for nuclear DNA staining.

After staining, the whole-mount or cryosection samples were mounted with Prolong Gold antifade medium (P36930, Thermo Fisher Scientific) at room temperature for 12 h. Samples were scanned using a Nikon C2 or Nikon NiE-A1 Plus confocal microscope, and ImageJ software was used to process the confocal images.

Cell quantification and statistical analysis

Before immunofluorescence staining, each cochlear sample was grossly separated into three portions of distinct lengths, and each portion of the same cochlea was initially scanned using a confocal microscope at low magnification (10× lens). After calculating the total length of each cochlea, the cochlear sample was precisely divided into basal, middle, and apical turns of equal length. Subsequently, for cell counting in experiments (Figure 1-figure supplement 2D), an ∼200 μm stretch of the sensory epithelium in each turn was scanned using a confocal microscope at high magnification (60× lens) and the numbers of HCs were determined. In Pou4f3-/- cochleae, the percentage of surviving HCs was calculated by normalizing the number of remaining HCs against their counterparts in WT mice. All cell numbers are presented as means ± SD. For statistical analyses, we used GraphPad Prism 6.0 software and performed Student’s t tests with Bonferroni correction.

Supporting information